Follow-up Samples

### 2017-01-13 submission/manuscript_outline_20161024.Rmd
add Fig 4 and S4 to manuscript results

***Differences in Adenoma and Carcinoma of Previously Associated Cancer Bacteria***
We next examined whether there were and differences in previously well described carcinoma associated OTUs.  These included the OTUs that aligned with Porphyromonas asaccharolytica (`r unique(filter(crc_bug_info, tax_id == "Porphyromonas")[, "otu"])`), Fusobacterium nucleatum (`r unique(filter(crc_bug_info, tax_id == "Fusobacterium")[, "otu"])`), Parvimonas micra (`r unique(filter(crc_bug_info, tax_id == "Parvimonas")[, "otu"])`), and Peptostreptococcus stomatis (`r unique(filter(crc_bug_info, tax_id == "Peptostreptococcus")[, "otu"])`).  First, the carcinoma samples showed a significant difference between initial and follow up samples for Peptostreptococcus stomatis (P-value = `r format(pvalue_adn_crc_summary["pept", "crc_BH"], digits = 3)`) and Porphyromonas asaccharolytica (P-value = `r format(pvalue_adn_crc_summary["porp", "crc_BH"], digits = 3)`) whereas there were no signficant differences in any of these OTUs in the adenoma samples [Table S4]. Second, when these OTUs were present, there was a clear magnitude difference in these specific OTUs based on whether they were from adenoma or carcinoma individuals [Figure 2].  However, only a small percentage of those with adenoma or carcinoma were positive for any of these OTUs.

@@

***Positive Probability Prediction after Surgical Removal of Adenoma or Carcinoma***

>>>>

***Differences in Adenoma and Carcinoma of Previously Associated Cancer Bacteria***
We next examined whether there were differences in previously well described carcinoma associated OTUs.  These included the OTUs that aligned with Porphyromonas asaccharolytica (`r unique(filter(crc_bug_info, tax_id == "Porphyromonas")[, "otu"])`), Fusobacterium nucleatum (`r unique(filter(crc_bug_info, tax_id == "Fusobacterium")[, "otu"])`), Parvimonas micra (`r unique(filter(crc_bug_info, tax_id == "Parvimonas")[, "otu"])`), and Peptostreptococcus stomatis (`r unique(filter(crc_bug_info, tax_id == "Peptostreptococcus")[, "otu"])`).  First, the carcinoma samples showed a significant difference between initial and follow up samples for Peptostreptococcus stomatis (P-value = `r format(pvalue_adn_crc_summary["pept", "crc_BH"], digits = 3)`) and Porphyromonas asaccharolytica (P-value = `r format(pvalue_adn_crc_summary["porp", "crc_BH"], digits = 3)`) whereas there were no signficant differences in any of these OTUs in the adenoma samples [Table S4]. Second, when these OTUs were present, there was a clear magnitude difference in these specific OTUs based on whether they were from adenoma or carcinoma individuals [Figure 2].  However, only a small percentage of those with adenoma or carcinoma were positive for any of these OTUs.

@@

***Positive Probability Prediction after Surgical Removal of Adenoma or Carcinoma***
Regardless of model used there was a significant decrease in the positive probability of either the sample being lesion or an initial sample on follow up (full lesion P-value = `r format(filter(all_probs_paired_wilcox, model_type =="lesion" & comparison == "lesion")[, "BH_correction"], scientific = TRUE, digits = 3)`, reduced lesion P-value = `r format(filter(all_probs_paired_wilcox, model_type =="red_lesion" & comparison == "lesion")[, "BH_correction"], scientific = TRUE, digits = 3)`, initial and follow up P-value = `r format(filter(all_probs_paired_wilcox, model_type =="IF" & comparison == "lesion")[, "BH_correction"], scientific = TRUE, digits = 3)`, and reduced initial and follow up P-value = `r format(filter(all_probs_paired_wilcox, model_type =="red_IF" & comparison == "lesion")[, "BH_correction"], scientific = TRUE, digits = 3)`).  The lesion model correctly kept the one individual who still had a carcinoma on follow up above the cut off point [Figure 4a & S4a] for a positive call while the initial and follow up model did not [Figure 4b & S4b].
